\sysfull

### 2018-04-12 paper/intro.tex
capybara reference added

Energy-harvesting devices create unique challenges because they operate {\em
intermittently} when energy is
available~\citep{hicks_isca_2017,lucia_snapl_2017}. An energy-harvesting device
buffers energy in a small storage capacitor~\citep{gorlatova_tmc_2013,gunduz_commag_2014} and operates when a
threshold amount of energy has accumulated. 
%
Harvestable energy sources are low-power (e.g., nW to $\mu$W) compared to a platform's operating
power level (hundreds of $\mu$W to mW). A device operates briefly until it depletes its buffered energy, after which, the device shuts
down and recharges to operate again later. As an example, recharge times may be
tens of seconds in radio frequency powered medical device~\cite[Fig.
3c]{nadeau_naturebio_2017}.  The recharge and discharge time --- which corresponds to the device's inactive and active time --- varies with the energy buffering capacitor's~\cite{capybara} and some devices fail and restart operating $\approx$10 to
$\approx$100 times per second~\citep{tan_infocom_2016,mementos,nvp}.

%\begin{figure}
%	\begin{subfigure}[t]{.35\linewidth}
%		\centering\large Figure
%		\caption{\centering WISP~\citep{wisp} against an RFID antenna}\label{fig:1a}
%	\end{subfigure}%
%	\begin{subfigure}[t]{.65\linewidth}
%		\centering\large Figure
%		\caption{\centering Program X~\citep{hicks_mibench2_2016} (split into X and Y tasks~\citep{chain}) at two distances}\label{fig:1b}
%    \end{subfigure}
%	\caption{Impact of an inadequate task sizing on the computation speed of a moving transiently-powered device.}\label{fig:1}
%\end{figure}

@@

%\textcolor{red}{tictpl is not HW, is it? also it doesn't deal with inconsistency; this paragraph doesn't include Hibernus, so it should not include CPTL either.}

% <<<<<<< HEAD
% \begin{figure}
% 	\includegraphics[width=.5\columnwidth]{figures/alpaca-war.pdf}
% 	\caption{\label{fig:virtualization}Adaptive task division at run-time might lead to write-after-read dependencies (variable \ttfamily{x}) that do not exist with static task division.\todo{Box with Task 1,2,3 must be the same size as merged task; Merged task must be named as Task 4; x must be marked in text as having WAR; "Task X" name should be next to the task box; "Window" - small letter}{Sinan}}
% \end{figure}
% =======

%Moved intel note to related work
\textbf{Task Decomposition of Intermittent Programs.} {\em
Task-based} programming and execution models require a
programmer~\citep{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to
statically decompose a program into a collection of {\em tasks}.  A task can
include arbitrary computation and these existing systems guarantee that each
tasks executes {\em atomically}, despite arbitrarily-timed power failures.  
%
The programmer explicitly expresses task-to-task control flow, or the compiler
converts existing program control-flow into task-to-task control flow to sequence 
the tasks that it defines.
%
Figure~\ref{fig:coalesce} (top) illustrates how a program's tasks execute and
shows how tasks can impose a run-time overhead. 
%
At each task transition, the system incurs an overhead to track and atomically
commit modifications to the non-volatile memory, to maintain consistency of
program state~\citep{chain,alpaca}.  
%
The more task transitions a program executes at run time, the more overhead.

@@

%Brandon: I moved Cleancut to the related work section.  THere's too much in the intro already

@@

%
%variables in non-volatile memory at \emph{run-time} that can
%break the atomicity of the \emph{virtual task}. Consider the
%example depicted in Fig.~\ref{fig:virtualization}: Tasks 1,
%2 and 3 being executed consecutively. All tasks in this
%example are atomic since they do not have WAR dependency on
%the persistent variables they are accessing, e.g. \emph{x}
%is only read and \emph{y} is only written within Task 1.
%Now, suppose three tasks have been virtualized into a single
%one at run-time, namely Task 4: since \emph{x} is now first
%\emph{read} and then \emph{written}, a WAR dependency on
%\emph{x} is introduced dynamically at
%run-time---unfortunately Task 4 is \emph{no more atomic}
%since its re-execution will not always produce the same
%results.
%
%Brandon: Sentence too long.
While a compiler can use static data privatization and commit instrumentation
(i.e., redo-logging) to eliminate statically identifiable, inter-task data
dependences~\citep{alpaca}, a \emph{dynamic} dependence between two coalesced
tasks requires dynamic privatization and commit actions. 
%
To ensure consistency and respect inter-task dependences, \sys uses a novel
approach to \emph{memory virtualization} that buffers non-volatile variable
updates in volatile memory during coalesced task execution, before committing
them to non-volatile memory at the dynamic task boundary.
%
%Therefore, we require a \emph{new execution
%model} that keeps each virtual task atomic by committing the
%modified persistent variables at the boundary defined
%dynamically at run-time---keeping the non-volatile memory
%unmodified upon a power-interrupt and preserving its
%consistency.

>>>>

Energy-harvesting devices create unique challenges because they operate {\em
intermittently} when energy is
available~\citep{hicks_isca_2017,lucia_snapl_2017}. An energy-harvesting device
buffers energy in a small storage capacitor~\citep{gorlatova_tmc_2013,gunduz_commag_2014} and operates when a
threshold amount of energy has accumulated. Harvestable energy sources are low-power (e.g., nW to $\mu$W) compared to a platform's operating
power level (hundreds of $\mu$W to mW). A device operates briefly until it depletes its buffered energy, after which, the device shuts
down and recharges to operate again later. As an example, recharge times may be
tens of seconds in radio frequency powered medical device~\cite[Fig.
3c]{nadeau_naturebio_2017}.  The recharge and discharge time---which corresponds to the device's inactive and active time---varies with the energy buffering capacitor's~\cite{capybara} and some devices fail and restart operating $\approx$10 to
$\approx$100 times per second~\citep{tan_infocom_2016,mementos,nvp}.

@@

\textbf{Task Decomposition of Intermittent Programs.} {\em
Task-based} programming and execution models require a
programmer~\citep{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to
statically decompose a program into a collection of {\em tasks}.  A task can
include arbitrary computation and these existing systems guarantee that each
tasks executes {\em atomically}, despite arbitrarily-timed power failures.  
%
The programmer explicitly expresses task-to-task control flow, or the compiler
converts existing program control-flow into task-to-task control flow to sequence 
the tasks that it defines.
%
Figure~\ref{fig:coalesce} (top) illustrates how a program's tasks execute and
shows how tasks can impose a run-time overhead. 
%
At each task transition, the system incurs an overhead to track and atomically
commit modifications to the non-volatile memory, to maintain consistency of
program state~\citep{chain,alpaca}.  
%
The more task transitions a program executes at run time, the more overhead.

@@

@@

%variables in non-volatile memory at \emph{run-time} that can
%break the atomicity of the \emph{virtual task}. Consider the
%example depicted in Fig.~\ref{fig:virtualization}: Tasks 1,
%2 and 3 being executed consecutively. All tasks in this
%example are atomic since they do not have WAR dependency on
%the persistent variables they are accessing, e.g. \emph{x}
%is only read and \emph{y} is only written within Task 1.
%Now, suppose three tasks have been virtualized into a single
%one at run-time, namely Task 4: since \emph{x} is now first
%\emph{read} and then \emph{written}, a WAR dependency on
%\emph{x} is introduced dynamically at
%run-time---unfortunately Task 4 is \emph{no more atomic}
%since its re-execution will not always produce the same
%results.

While a compiler can use static data privatization and commit instrumentation
(i.e., redo-logging) to eliminate statically identifiable, inter-task data
dependences~\citep{alpaca}, a \emph{dynamic} dependence between two coalesced
tasks requires dynamic privatization and commit actions. 
%
To ensure consistency and respect inter-task dependences, \sys uses a novel
approach to \emph{memory virtualization} that buffers non-volatile variable
updates in volatile memory during coalesced task execution, before committing
them to non-volatile memory at the dynamic task boundary.
%
%Therefore, we require a \emph{new execution
%model} that keeps each virtual task atomic by committing the
%modified persistent variables at the boundary defined
%dynamically at run-time---keeping the non-volatile memory
%unmodified upon a power-interrupt and preserving its
%consistency.
